Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-29 paper_jasa.tex
subject specific power from model
cleaning up definitions still, now stuck

\begin{dfn}\label{dfn:test}
\red{why do we need the $\theta$? - it's not defined and not explained. usually we would assume that lineups are non-parametric}
The \textbf{visual test}, $V_{\theta}$, is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if `enough' observers select the observed data plot in the lineup of $m$ plots, and
\item \textbf{Fail to reject} $H_0$  otherwise. %if the observer selects a null plot.
\end{itemize}
where `enough' observers is defined as some threshold $x_{1-\alpha}$, for which $P(X \ge x_{1-\alpha}) < \alpha$, the level of significance.
\end{dfn}

\blue{To avoid confusion with one tailed $(1-\alpha)$ vs two tailed $(1-\alpha/2)$ notation, can we just use $x_{\alpha}$? }

\red{alternative definition of visual test where $type-I$ error $\alpha$ is attached.

@@

Notice that now we can fix $type-I$ error to some values even less than $1/m$ by increasing $K$. $type-I$ error is $1/m$ only when $K=1$.
}

@@

\begin{dfn}\label{dfn:error}
The \textbf{Type I error} is the probability of rejecting $H_0$ when it is true, the probability for that is $P(X \ge x_{1-\alpha})$, which is controlled by $\alpha$.
% identifying the observed data plot, when $H_0$ is true, which is $1/m$, and is thus controlled by the number of null plots. 
\textbf{Type II error} is the probability of failing to identify the observed data plot, when $H_0$ is not true, $P( X <  x_{1-\alpha})$, where $x_{1 - \alpha}$ is the (approximate) $1-\alpha$ quantile of  $B_{K, 1/m}$.
\end{dfn}

\green{Why are we including $x_{1-\alpha}$ in both sides?}
\red{fixed  now-- $X < x_{1 - \alpha}$ is the acceptance region, $X \ge x_{1-\alpha}$ is rejection region.}

\noindent Because $X$ takes only discrete values we can not always control exactly for $\alpha$, finding an exact $x_{1-\alpha}$. For example, when there is only one observer, $1/m$ is the minimal value at which we can set $\alpha$.

\green{check that we consistently use $1/m$, or $\frac{1}{m}$ in the text.} \blue{its jasa guideline to use fraction like $1/m$ whenever possible to save space}.

@@

\green{Why???? Under the alternative hypothesis, we have to account for different visual abilities of  individuals:} 
\red{I think that's more a matter of writing it - sorry for the confusion - }

let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise, \red{where $p_i$ is the probability that individual $i$ picks out the data plot from the lineup. 
If all individuals have the same probability $p$ for picking out the data plot, $X = \sum_i X_i$ has distribution $\text{Binom}(K, p)$, and we can estimate $p$ as $\hat{p} = x/K$, where $x$ is the number of observers (out of $K$), who pick out the data plot from the lineup.

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_exp1.pdf}}
       \caption{Observed power shown by loess smoother and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_loess1}
\end{figure*}

>>>>

%\begin{dfn}\label{dfn:test}
%\red{why do we need the $\theta$? - it's not defined and not explained. usually we would assume that lineups are non-parametric}
%The \textbf{visual test}, $V_{\theta}$, is defined to be 
%\begin{itemize}\itemsep-3pt
%\item \textbf{Reject} $H_0$ if `enough' observers select the observed data plot in the lineup of $m$ plots, and
%\item \textbf{Fail to reject} $H_0$  otherwise. %if the observer selects a null plot.
%\end{itemize}
%where `enough' observers is defined as some threshold $x_{1-\alpha}$, for which $P(X \ge x_{1-\alpha}) < \alpha$, the level of significance.
%\end{dfn}

%\blue{To avoid confusion with one tailed $(1-\alpha)$ vs two tailed $(1-\alpha/2)$ notation, can we just use $x_{\alpha}$? }

%\red{alternative definition of visual test where $type-I$ error $\alpha$ is attached.

@@

@@

\begin{dfn}\label{dfn:error}
The \textbf{Type I error} is the probability of rejecting $H_0$ when it is true, the probability for that is $P(X \ge x_{\alpha})$, which is controlled by $\alpha$.
% identifying the observed data plot, when $H_0$ is true, which is $1/m$, and is thus controlled by the number of null plots. 
\textbf{Type II error} is the probability of failing to identify the observed data plot, when $H_0$ is not true, $P( X <  x_{\alpha})$, where $x_{\alpha}$ is the (approximate) $\alpha$ quantile of  $B_{K, 1/m}$. \green{Is this Binom????}
\end{dfn}

\noindent Because $X$ takes only discrete values we can not always control exactly for $\alpha$, finding an exact $x_{\alpha}$. For example, when there is only one observer, $1/m$ is the minimal value at which we can set $\alpha$. It can be set to be smaller, even arbitrarily small, by increasing $K$.

\green{check that we consistently use $1/m$, or $\frac{1}{m}$ in the text.} \blue{its jasa guideline to use fraction like $1/m$ whenever possible to save space}. \green{so please make sure that they are all $1/m$.}

@@

\green{What does this part apply to ???? power?}let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise, \red{where $p_i$ is the probability that individual $i$ picks out the data plot from the lineup. 
If all individuals have the same probability $p$ for picking out the data plot, $X = \sum_i X_i$ has distribution $\text{Binom}(K, p)$, and we can estimate $p$ as $\hat{p} = x/K$, where $x$ is the number of observers (out of $K$), who pick out the data plot from the lineup.

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_exp1.pdf}}
       \caption{Observed power shown by loess smoother and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_effect1}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_subject_exp1.pdf}}
       \caption{Subject specific power obtained from equation \ref{eqn:effect} and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_effect_subject1}
\end{figure*}
